---
title: "p8105_hw6_xg2451"
output: github_document
---

# Problem 1

```{r message=FALSE}
library(dplyr)
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") |> 
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |> 
  select(name, id, everything())
```
#### Perform Bootstrap Sampling and Fit Linear Regression Models
```{r message=FALSE}
library(tidyr)
library(modelr)
library(tidyverse)
library(purrr)
library(broom)

set.seed(123)
boot_fit <- weather_df |> 
  modelr::bootstrap(n = 5000)  |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin, data = df)),
    # Extract regression coefficients
    results = map(models, broom::tidy),
    # Extract model summary statistics r^2
    glance = map(models, broom::glance)
  ) |> 
  select(-strap, -models)
```

#### Extract and Compute $r^2$ and log($\hat{\beta}_0\times\hat{\beta}_1$)
```{r}
boot_summary <- boot_fit |> 
  mutate(
    # Extract r^2 
    r_squared = map_dbl(glance, \(g) g$r.squared),
    # Compute log(beta0 * beta1)
    log_beta_product = map_dbl(results, \(res) {
      beta_0 <- res |> filter(term == "(Intercept)") |> pull(estimate)
      beta_1 <- res |> filter(term == "tmin") |> pull(estimate)
      log(beta_0 * beta_1)
    })
  )
```

#### Plot the Distributions of $r^2$ and log($\hat{\beta}_0\times\hat{\beta}_1$)
```{r}
library(ggplot2)
# Plot the distribution of r^2
ggplot(data = data.frame(r_squared = boot_summary$r_squared), aes(x = r_squared)) +
  geom_density() +
  labs(
    title = "Distribution of r-squared",
    x = "r-squared",
    y = "Density"
  )
```
```{r}
# Plot the distribution of log(beta0 * beta1)
ggplot(data = data.frame(log_beta_product = boot_summary$log_beta_product), aes(x = log_beta_product)) +
  geom_density() +
  labs(
    title = "Distribution of log(beta0 * beta1)",
    x = "log(beta0 * beta1)",
    y = "Density"
  )
```

**Description:**

Both distributions show relatively low variability, indicating that the regression model's performance metrics and parameter estimates are stable under resampling. The high concentration of $r^2$ near 0.92 confirms a strong model fit, while the narrow range of log($\hat{\beta}_0\times\hat{\beta}_1$) implies consistent relationships between the predictor and response.
 
#### Compute 95% Confidence Intervals

```{r}
r_squared_ci <- quantile(boot_summary$r_squared, c(0.025, 0.975))
log_beta_product_ci <- quantile(boot_summary$log_beta_product, c(0.025, 0.975))
```
For estimates of \(r^2\), the 95% confidence interval is `r sprintf("(%.3f, %.3f)", r_squared_ci[1], r_squared_ci[2])`. 

For estimates of \(\log(\hat{\beta}_0 \cdot \hat{\beta}_1)\), the 95% confidence interval is `r sprintf("(%.3f, %.3f)", log_beta_product_ci[1], log_beta_product_ci[2])`.





















